Workflow

### 2020-02-19 r/Workflow.Rmd
feb updates

---
title: "Workflow"
author: "Molly Wilson"
date: "5/8/2019"
output: html_document
---

@@

3. Exploration/analysis files:
  - **Data_prodding.rmd**: exploring relationships among variables, distributions, etc.
  - **Analysis.rmd**: initial boxplots/bargraphs looking at trends among islands/sites, testing ANOVAs/assumptions, predicted grazing impact, bite content calculations
  - **Models.rmd**: PCAs, LMEs, GAMMs (exploratory, no .csv exports)
  - **Ch2_outline_V3**: selected analyses for current manuscript outline

>>>>

---
title: "Workflow"
author: "Molly Wilson"
date: "5/8/2019"
output: html_document

---

@@

3. Exploration/analysis files:
  - **Data_prodding.rmd**: exploring relationships among variables, distributions, etc.
  - **Analysis_misc.rmd**: initial boxplots/bargraphs looking at trends among islands/sites, testing ANOVAs/assumptions, predicted grazing impact, bite content calculations
  - **Models.rmd**: PCAs, LMEs, GAMMs (exploratory, no .csv exports)
  - **Paper_analyses**: selected analyses for current manuscript outline, as well as relevant precursors (checking sample sizes, testing for normality, etc.)
